Component-Based mruby Platform for IoT Devices

### 2017-11-15 ipsj/paper.tex
Add Acknowledgments
Add Abstract

@@

\begin{acknowledgment}

\end{acknowledgment}

>>>>

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework can call Tomakomai InterNETworking (TINET), a Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stack for use in embedded systems, functions from mruby programs.
In addition, this paper proposes two component-based functionality such as a componentized TINET--TINET+TECS--and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator--TLSF+TECS--.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionality.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
The results of an experimental comparison between the proposed component-based and original TINETs show that the execution time and memory consumption overhead are reduced and the configurability is improved.

@@

\begin{acknowledgment}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
The authors would like to thank Hiroaki Nagashima and Kazuaki Tanaka for supporting this research.
\end{acknowledgment}
